%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Acknowledgments}

I would like to thank the following:
My advisor, Karthik Pattabiraman, for giving me the opportunity to pursue my ideas and explore during my masters which was my original goal. I've learned a lot from him. 

Margo Seltzer for being a constant source of inspiration that helped me pursue my ideas fearlessly and enjoy research during my masters. Without her this thesis would not have been possible. 

Syed Mubashir Iqbal for collaborating on this work and teaching me a bunch of stuff; working with Mubashir was one of the most fun experiences of my masters thesis because of the infinite all nighters we pulled off to finish the experiments in ICICS 348. 

Mark Greenstreet, Alan Hu, Hassan Halawa, Akshay Gopalakrishnan and Puneet Mehrotra for patiently listening to my half-baked ideas in the initial stages of the work that eventually lead me to find my own path. 

William Bowman for introducing me to the world of abstractions that helped me understand my own work a little better.  

Members of computer systems reading group and static analysis reading group for interesting discussions that might have directly or indirectly influenced my thinking. 

The multiple travel granting committees from conferences that gave me the opportunity to have many many interesting discussions with researchers all around the world which might have significantly influenced my thinking. 

Members of Dependable Systems and Systopia (previously known as NSS) Lab for multiple fun hangouts. 

The library staff at UBC for always ordering the books I've asked for as soon as possible.

The night working staff at UBC with whom I had multiple late night conversations about random things to take a break from work. 


All my friends (y'all know who you are) for being there; listening to my constant bicker about life despite being in different timezones.   

Tom Lee music store for letting me use their jam room for hours and hours every week since 2018. Surviving the journey without music would be impossible. 

My ma and sister for being ok (or maybe pretending to be ok) with my new life plan every other week, thus never holding me back. 




